\section{Conclusion}

\glspl{MSR} feature significant multiphysics interactions which present
computational challenges for many existing multiphysics reactor analysis
software. This chapter presents code-to-code verification of Moltres
capabilities in modeling such multiphysics phenomena in fast-spectrum
\glspl{MSR} based on the CNRS benchmark \cite{tiberga_results_2020}.
The CNRS benchmark assesses multiphysics \gls{MSR} simulation
software through several steps involving single-physics and coupled
neutronics/thermal-hydraulics problems.

The results showed that Moltres is consistent with the participating software
presented in the CNRS benchmark paper for the modeling of important phenomena
in fast-spectrum \glspl{MSR}. The percentage discrepancies in the various
neutronics, velocity, and temperature quantities mostly fall below or within
one standard deviation of the average of the benchmark participants.
Minor deviations in the temperature in Steps 0.3 and 1.2 
stem from the discontinuous velocity
boundaries on the top corners in the lid-driven cavity flow. We have shown that
these deviations are limited to the top boundary of the domain and do not
affect the rest of the physical parameters. The results from
Moltres agree closest with the TUD-S$_2$ software package, which implements the
$S_2$ discrete ordinates method for
neutron transport on a uniform structured mesh with a \gls{DFEM}-based solver.
These features make Moltres the most similar to the TUD-$S_2$ model as compared
to the other models which employ different neutron transport models,
non-uniform meshes, and/or finite volume-based solvers.

This work verifies Moltres' capabilities for future work involving modeling and
simulation of fast-spectrum \glspl{MSR} such as the European \gls{MSFR} and
TerraPower's \gls{MCFR} \cite{terrapower_terrapower_2021}. Notably, the CNRS
benchmark does not assess modeling capabilities for complex physics phenomena
such as turbulent flow in \glspl{MSR}. This worked in favor of verifying
existing capabilities in Moltres since Moltres does not currently support
turbulence modeling. However, we expect coolant loops in many \gls{MSR} designs
will experience turbulent flow under normal operation or accident scenarios.
These expectations, alongside the subpar results of pump-initiated accidents
reported in Section \ref{sec:msfr}, call for the implementation and
verification of a turbulence model in Moltres for accurate modeling of
\glspl{MSR}.

\FloatBarrier
